Analysis

### 2022-08-02 production/prod_analysis-fix-t5.Rmd
submission

# create plot-------------------------------------------------------------------
if (!require("pacman")) install.packages("pacman")
pacman::p_load(cowplot)
s <- 0.35
m <- 0.6
l <- 0.7
#Final plot
title <- cowplot::ggdraw() + 
  cowplot::draw_label(
    "Figure 1: Frequencies for Conviviality, Identity and Threat items",
    fontface = 'bold',
    size = 15,
    x = 0,
    hjust = 0
  )

likert1<-   
  cowplot::add_sub(
    cowplot::plot_grid(title,p_ansied,p_simpat,p_convi,p_simili,p_identi,p_threat, 
                       align = "hv",
                       axis = "a",
                       nrow = 6, #4 plots
                       ncol = 1, #1 column   
                       rel_heights = c(0.1,s,s,m,s,m,s) #fig size within plot
    ),
    label = paste0("Source: Own elaboration based on ELSOC Survey",
                   " (n=",dim(na.omit(df_study1))[1],")"
    ),        # Caption: source and sample size
    size = 12,  # Caption font size
    hjust = -0.25# Caption align  
  ) %>%
  cowplot::ggdraw()  
# likert1
ggplot2::ggsave(filename = "figure1.jpg",
                plot = likert1,
                path = here::here("output/images"),
                device = "jpg",
                units = "cm",
                scale = 3.5,
                width = 10,height = 10)
pacman::p_load(cowplot)

>>>>

# create plot-------------------------------------------------------------------
if (!require("pacman")) install.packages("pacman")
pacman::p_load(cowplot)
s <- 0.4
m <- 0.6
l <- 0.8
#Final plot
title <- cowplot::ggdraw() + 
  cowplot::draw_label(
    "Figure 1: Frequencies for Conviviality, Identity and Threat items",
    fontface = 'bold',
    size = 15,
    x = 0,
    hjust = 0
  )

likert1<-   
  cowplot::add_sub(
    cowplot::plot_grid(title,p_ansied,p_simpat,p_convi,p_simili,p_identi,p_threat, 
                       align = "hv",
                       axis = "a",
                       nrow = 7, #4 plots
                       ncol = 1, #1 column   
                       rel_heights = c(s,s,0.35,m,s,m,s) #fig size within plot
    ),
    label = paste0("Source: Own elaboration based on ELSOC Survey",
                   " (n=",dim(na.omit(df_study1))[1],")"
    ),        # Caption: source and sample size
    size = 12,  # Caption font size
    hjust = -0.25# Caption align  
  ) %>%
  cowplot::ggdraw()  
# likert1
ggplot2::ggsave(filename = "figure1.jpg",
                plot = likert1,
                path = here::here("output/images"),
                device = "jpg",
                units = "cm",
                scale = 3.5,
                width = 10,height = 10)
